A pair of co-moving, Sun-like stars with different chemical abundances:\\ a possible signature of copious rocky accretion (needs work)

### 2017-04-21 paper/ms.tex
typo city

Surface lithium abundance in a sun-like star such as \sunanalog\ decreases with its age
due to mixing induced by convection or rotation which brings lithium
into the interior ($T>2.5 \times 10^{6}$~K)
where it will be destroyed by proton capture burning.
Thus, surface lithium abundance is an indicator of stellar ages.
The $\elem{Li}$ abundance of $2.25$ for \sunanalog\ implies an age of $\lesssim 1$~Gyr
according to the theoretical models tuned to explain the solar lithium abundance
and rotational profile (\citealt{2005Sci...309.2189C}).
The lithium abundance of \bizarreone\ is still higher by $0.5$~dex
showing the largest difference among all measured elements.
Given the overall higher metal abundances and the peculiar abundance patterns in \bizarreone,
it is unclear, however, whether this higher $\elem{Li}$ abundance
means a younger age or something else.
For example, the presence of $\elem{Li}$-rich red giant stars has been attributed
to the engulfment of substellar companions such as gas giant planets are brown dwarfs
which may replenishe unburnt $\elem{Li}$ (\citealt{Casey:2016aa}).
We come back to the $\elem{Li}$ difference later in our discussion.

>>>>

Surface lithium abundance in a sun-like star such as \sunanalog\ decreases with its age
due to mixing induced by convection or rotation which brings lithium
into the interior ($T>2.5 \times 10^{6}$~K)
where it will be destroyed by proton capture burning.
Thus, surface lithium abundance is an indicator of stellar ages.
The $\elem{Li}$ abundance of $2.25$ for \sunanalog\ implies an age of $\lesssim 1$~Gyr
according to the theoretical models tuned to explain the solar lithium abundance
and rotational profile (\citealt{2005Sci...309.2189C}).
The lithium abundance of \bizarreone\ is still higher by $0.5$~dex
showing the largest difference among all measured elements.
Given the overall higher metal abundances and the peculiar abundance patterns in \bizarreone,
it is unclear, however, whether this higher $\elem{Li}$ abundance
means a younger age or something else.
For example, the presence of $\elem{Li}$-rich red giant stars has been attributed
to the engulfment of substellar companions such as gas giant planets or brown dwarfs
which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
We come back to the $\elem{Li}$ difference later in our discussion.
